{\large Gravitational wave sources in our Galactic backyard:}\\{\normalsize Predictions for BHBH, BHNS and NSNS binaries in \emph{LISA}

### 2021-11-12 paper/tex/sections/results.tex
all Neige email comments done

We further note that the detectable population is concentrated on the left side of LISA's sensitivity window. The peak is located at a frequency of about $0.4 \unit{mHz}$, which is much lower than the frequency where LISA will be most sensitive (about $10 \unit{mHz}$). This can be understood as an evolutionary effect. DCOs typically form with wide orbits (low frequencies) that would not be detectable yet. Their orbits shrink as they lose angular momentum in the form of gravitational waves leading to an increase of their orbital frequency until they become detectable. These systems are increasingly rare because they evolve faster and faster towards higher frequency as the inspiral accelerates, even though the signal emitted by a more compact binary is stronger \citep{Peters+1964}. The vertical grid lines show these rapidly decreasing inspiral times at increasing frequencies. Most of the population is thus expected to reside at low frequencies.

@@

There is a distinct subpopulation of binaries, most clearly visible in the lower panels as an offshoot that extend downwards to ASDs of $10^{-19} \unit{Hz}^{-1/2}$, especially around $2 \unit{mHz}$. This offshoot is almost uniquely composed of eccentric binaries, as can be seen in Fig.~\ref{fig:dcos_on_sc_ecc_col} in our appendix, which shows a similar figure but colouring individual systems by their eccentricity. This can also be seen, albeit indirectly, from the contours shown in the bottom panels of Fig.~\ref{fig:dcos_on_sc}, which encompass 90\% of the \textit{circular} sources in each population. This contour does not include the offshoot. We conclude that eccentric sources occupy a very different region in this diagram.

@@

\begin{figure*}[t]
    \centering
    \includegraphics[width=\textwidth]{fig3_detectable_properties_4yr.pdf}
    \caption{Properties of detectable systems for a 4-year LISA mission in our fiducial model. Each panel shows a kernel density estimator for a single property, coloured by DCO type. The shaded areas show the 1- and 2-$\sigma$ uncertainties (obtained via bootstrapping). The dotted lines in the black hole mass panel show the individual primary and secondary mass distributions. See Sec.~\ref{sec:fiducial_distributions} for a discussion. \href{https://github.com/TomWagg/detecting-DCOs-in-LISA/blob/main/paper/figures/fig3_detectable_properties_4yr.pdf}{\faFileImage} \href{https://github.com/TomWagg/detecting-DCOs-in-LISA/blob/main/paper/figure_notebooks/fiducial.ipynb}{\faBook}.}
    \label{fig:fiducial_pdf_distributions}
\end{figure*}

@@

@@

For systems with eccentricities higher than $e\gtrsim0.3$, most gravitational wave energy is emitted in higher harmonics. Such systems are more rare, but we find them to be significant among the BHBH population, where they account for \BHBHHighlyEccentric{} of systems.

These BHBHs that are still eccentric when reaching the LISA band are primarily systems formed through the stable mass transfer channel \citep{vandenHeuvel+2017}. These systems are still relatively wide just prior to formation of the second BH. If the kick is oriented roughly in opposite direction to the orbital motion and has a velocity that is of similar magnitude as the orbital velocity, it will lead to the formation of a highly eccentric system.

It is rare to get such a ``lucky kick'', but there are a few effects that favour this for BHBH. The kicks of BHs are reduced and they are thus less likely to disrupt the system.  Moreover, because of their higher masses, BHBHs can be observed already at lower orbital frequencies. This means that they have not had as much time to circularise and so still have significant eccentricity by the time of the LISA mission. Finally, LISA favours the detection of eccentric systems, if all other properties are held fixed. This is because the gravitational wave emission is stronger (Eq.~\ref{eq:peters_f}) and the energy is emitted at higher frequencies \citep[Eq.~20]{Peters+1963} where LISA is more sensitive.

@@

When comparing the distribution of formation times for the three different DCO types we see that NSNSs are most strongly concentrated at recent times, followed by BHBH and then BHNS. To understand this it is helpful to consider how the inspiral time scales with various parameters
\begin{equation}
    t_{\rm inspiral} \propto \frac{a^4}{(m_1 + m_2)^{3}} \cdot \frac{q}{(1+q)^2} \cdot (1 - e^2)^{-7/2}.
\end{equation}
The inspiral time depends most strongly on the separation at DCO formation ($a$) and this is where the three types also differ most strongly (see Fig.~\ref{fig:dco_formation_properties}). The NSNS systems have the tightest orbits at DCO formation. The median of the distribution of separations at DCO formation, $\langle a_{\rm DCO} \rangle_{\rm med}$, relate as 8:3:1 for BHBH:BHNS:NSNS in our simulations. This results in increase of the inspiral time by a factor of about 4000:80:1. The total masses affect the inspiral time to the third power and this where the heavier BHBH systems are favoured. The median total masses differ by ratios of 6:4:1 for BHBH:BHNS:NSNS in our simulations, impacting the inspiral times such that they are a factor of 200:60:1 shorter, partially counteracting the effect of the separations. The term depending on the mass ratio $q$ only varies by about 30\% for the mass ratio ranges considered here and so is not of interest. The eccentricity term is not of importance for mildly eccentric systems, $f(e_{\rm DCO} \le 0.3)  \le 1.4$ but of large importance for the very eccentric  $f(e_{\rm DCO} \ge 0.9) \ge 300$. The fraction of highly eccentric systems with $e_{\rm DCO}>0.9$ is 33\%, 16\$ and 8\% of for BHBH, BHNS and NSNS respectively, see also Fig.~\ref{fig:dco_formation_properties}.

@@

\paragraph{Time until merger} Fig.~\ref{fig:fiducial_pdf_distributions}f shows the remaining time until merger for each of the DCO types at the start of LISA mission. The distributions are strikingly similar and peak with merger times of around a Myr.

@@

\subsection{Distribution in the Milky Way}\label{sec:mw_detectable_distribution}
For our Milky way model we considered three different components, a low-$\alpha$ (``thin'') disc, an older high-$\alpha$ (``thick'') disc and a bulge/bar. In Table~\ref{tab:component_fractions} we summarise the number of detections originating from each of these components. Despite the fact that only $42.5\%$ of systems are formed in the low-$\alpha$ disc, we find that $86\%$ of the detections originate from this component. This is because most detectable systems were formed relatively recently (see Fig.~\ref{fig:fiducial_pdf_distributions}e) and so the high-$\alpha$ disc and bulge are effectively too old to contribute many detectable systems. Nevertheless, we do find a significant fraction of detectable systems originate in the high-$\alpha$ disc and bulge, indicating that it is still important to include these components, as was ignored in some earlier works (see Sec.~\ref{sec:compare_studies}).

@@

\subsection{Formation channels}\label{sec:progenitors_and_formation}
In our fiducial model, approximately two thirds of detectable BHBHs are formed through the `only stable mass transfer' channel \citep{vandenHeuvel+2017}, whilst the remaining third are primarly formed through the `classic' channel \citep{Bhattacharya+1991}. Detectable BHNSs follow an inverse pattern, such that around two thirds are formed through the `classic' channel and the rest are mainly formed through only stable mass transfer.

@@

\subsection{How accurately will we be able to infer the parameters of detected systems?}\label{sec:measurement_uncertainties}
So far we have discussed the properties of the detectable sources that can, in principle, be inferred from observations. However, many sources will only be barely detectable. Here we discuss for how many systems we expect to get high enough SNR to obtain accurate and useful measurements of these parameters. Below we discuss the expected SNR distribution and the typical uncertainties expected for the most relevant parameters, namely, the chirp mass and sky localisation.

@@

In Fig.~\ref{fig:snr_dist} we show the cumulative number of detections with a given SNR. Although many have SNRs around the our assumed detection threshold of 7, many systems are detection with very high SNRs. We find that for a 4(10)-year LISA mission, of the 124(202) detections, 85(138), 16(27) and 9(14) systems have SNRs greater than 10, 50 and 100 respectively. These high SNR systems are typically, but not only, the more massive BHBH systems.

@@

We find that for a 4(10)-year LISA mission, approximately 41(105) detections have measurable chirp masses ($\Delta \mathcal{M}_c / \mathcal{M}_c < 1$, indicated by the dark shaded region in Fig.~\ref{fig:m_c_unc}) whilst 13(31) have chirp mass uncertainties below 10\%. This uncertainty is generally dominated by the uncertainty on the time derivative of the frequency, since most of the binaries are too early in their inspiral for LISA to measure a strong chirp.

Note that increasing the mission length significantly increases the number of detections for which we can measure the mass. The total number of detections only scales as $\sqrt{T_{\rm obs}}$, yet we find that the total number of detections \textit{with well measured masses} scales approximately as $T_{\rm obs}$.

@@

We quantify the sky localisation of a source by estimating the angular resolution for the detectable sources. Since all potential sources are effectively stationary on the timescale of the LISA mission, which can follow \citet{Mandel+2018} and use the timing accuracy of LISA and the effective detector baseline to calculate the angular resolution, $\sigma_{\theta}$, as
\begin{equation}
    \sigma_{\theta} = 16.6^\circ \left(\frac{7}{\rho}\right) \left(\frac{5 \times 10^{-4} \unit{Hz}}{f_{\rm dom}}\right) \left( \frac{2 \unit{AU}}{L} \right),
\end{equation}
where $L$ is the effective detector baseline, which for LISA is 2 AU since it will orbit the Sun.

@@

For comparison, the size of a pencil beam for a $15 \unit{m}$ diameter SKA dish observing at 1.4 GHz is roughly 0.67 square degrees \citep{Smits+2009}, corresponding to an angular resolution of $\sigma_\theta = \sqrt{(0.67 / \pi)} = 0.46^\circ$ (similar to the angular size of the moon). We will further discuss the prospects of matching LISA detections to radio pulsars with SKA further in Sec.~\ref{sec:pulsar_matching}.

>>>>

We further note that the detectable population is concentrated on the left side of LISA's sensitivity window. The peak is located at a frequency of about $0.4 \unit{mHz}$, which is much lower than the frequency where LISA will be most sensitive (about $10 \unit{mHz}$). This can be understood from the acceleration of inspiraling DCOs as they evolve towards higher frequencies. DCOs typically form with wide orbits (low frequencies) that would not be detectable yet. Their orbits shrink as they lose angular momentum in the form of gravitational waves leading to an increase of their orbital frequency until they become detectable. These systems are increasingly rare because they evolve faster and faster towards higher frequency as the inspiral accelerates, even though the signal emitted by a more compact binary is stronger \citep{Peters+1964}. The vertical grid lines show these rapidly decreasing inspiral times at increasing frequencies. Most of the population is thus expected to reside at low frequencies.

@@

There is a distinct subpopulation of binaries, most clearly visible in the lower panels as an offshoot that extends downwards to ASDs of $10^{-19} \unit{Hz}^{-1/2}$, especially around $2 \unit{mHz}$. This offshoot is almost uniquely composed of eccentric binaries, as can be seen in Fig.~\ref{fig:dcos_on_sc_ecc_col} in our appendix, which shows a similar figure but colouring individual systems by their eccentricity. This can also be seen, albeit indirectly, from the contours shown in the bottom panels of Fig.~\ref{fig:dcos_on_sc}, which encompass 90\% of the \textit{circular} sources in each population. This contour does not include the offshoot. We conclude that eccentric sources occupy a very different region in this diagram.

@@

\begin{figure*}[t]
    \centering
    \includegraphics[width=\textwidth]{fig3_detectable_properties_4yr.pdf}
    \caption{Properties of detectable systems for a 4-year LISA mission in our fiducial model. Each panel shows a kernel density estimator for a single property, coloured by DCO type. The shaded areas show the 1- and 2-$\sigma$ uncertainties (obtained via bootstrapping). The dotted lines in panel b show the individual primary and secondary mass distributions. The dotted line in panel e shows the star formation history we have assumed in our Milky Way model. See Sec.~\ref{sec:fiducial_distributions} for a discussion. \href{https://github.com/TomWagg/detecting-DCOs-in-LISA/blob/main/paper/figures/fig3_detectable_properties_4yr.pdf}{\faFileImage} \href{https://github.com/TomWagg/detecting-DCOs-in-LISA/blob/main/paper/figure_notebooks/fiducial.ipynb}{\faBook}.}
    \label{fig:fiducial_pdf_distributions}
\end{figure*}

@@

% For both the BHBHs and BHNSs, we see that the black hole mass distribution favours low masses. About $90\%$ of BHs have masses below $11 \unit{M_{\odot}}$, in our fiducial simulations shown here. 
% Unlike the current network of ground-based GW observatories, LISA will be equally sensitive to inspiraling BHBHs throughout the entire Milky Way, regardless of their mass (given that all inspiraling BHBH pass through the LISA sensitivity band \todo{citation?}). 
% Hence we expect LISA to provide us with an unbiased view of the distribution of BH masses in inspiraling compact object binaries.

@@

For systems with eccentricities higher than $e\gtrsim0.3$, most gravitational wave energy is emitted in higher harmonics. Such systems are more rare, but we find them to be significant among the BHBH population, where they account for \BHBHHighlyEccentric{} of the systems.

The BHBHs that are still eccentric when reaching the LISA band are primarily systems formed through the stable mass transfer channel. %\citep{vandenHeuvel+2017}. 
These systems are still relatively wide just prior to formation of the second BH. If the kick is oriented roughly in opposite direction to the orbital motion and has a velocity that is of similar magnitude as the orbital velocity, it will lead to the formation of a highly eccentric system.

It is rare to get such a ``lucky kick'', but there are a few effects that favour this for BHBH systems. The kicks of BHs are reduced by fallback and they are thus less likely to disrupt the system.  Moreover, because of their higher masses, BHBHs can be observed already at lower orbital frequencies. This means that they have not had as much time to circularise and so still have significant eccentricity by the time of the LISA mission. Finally, LISA favours the detection of eccentric systems, if all other properties are held fixed. This is because the gravitational wave emission is stronger (Eq.~\ref{eq:peters_f}) and the energy is emitted at higher frequencies \citep[Eq.~20]{Peters+1963} where LISA is more sensitive.

@@

When comparing the distribution of formation times for the three different DCO types we see that NSNSs are most strongly concentrated at recent times, followed by BHBHs and then BHNSs. To understand this it is helpful to consider that the inspiral time scales with various parameters
\begin{equation}
    t_{\rm inspiral} \propto \frac{a^4}{(m_1 + m_2)^{3}} \cdot \frac{q}{(1+q)^2} \cdot (1 - e^2)^{-7/2}.
\end{equation}
The inspiral time depends most strongly on the separation at DCO formation ($a$) and this is where the three types also differ most strongly (see Fig.~\ref{fig:dco_formation_properties}). The NSNS systems have the tightest orbits at DCO formation. The median of the distribution of separations at DCO formation, $\langle a_{\rm DCO} \rangle_{\rm med}$, relate as 8:3:1 for BHBH:BHNS:NSNS in our simulations. This results in increase of the inspiral time by a factor of about 4000:80:1. The total masses affect the inspiral time to the third power and this where the heavier BHBH systems are favoured. The median total masses differ by ratios of 6:4:1 for BHBH:BHNS:NSNS in our simulations, impacting the inspiral times such that they are a factor of 200:60:1 shorter, partially counteracting the effect of the separations. The term depending on the mass ratio $q$ only varies by about 30\% for the mass ratio ranges considered here and so is not of interest. The eccentricity term is not of importance for mildly eccentric systems, $f(e_{\rm DCO} \le 0.3)  \le 1.4$ but of large importance for the very eccentric  $f(e_{\rm DCO} \ge 0.9) \ge 300$. The fraction of highly eccentric systems with $e_{\rm DCO}>0.9$ is 33\%, 16\%, and 8\% of for BHBH, BHNS and NSNS respectively, see also Fig.~\ref{fig:dco_formation_properties}.

@@

\paragraph{Time until merger} Fig.~\ref{fig:fiducial_pdf_distributions}f shows the remaining time until merger for each of the DCO types at the start of LISA mission. The distributions are strikingly similar and peak with merger times of around one Myr.

@@

\subsection{Distribution in the Milky Way}\label{sec:mw_detectable_distribution}
For our Milky way model we considered three different components, a low-\achem~(``thin'') disc, an older high-\achem~(``thick'') disc and a bulge/bar. In Table~\ref{tab:component_fractions} we summarise the number of detections originating from each of these components. Despite the fact that only $42.5\%$ of systems are formed in the low-\achem~disc, we find that $86\%$ of the detections originate from this component. This is because most detectable systems were formed relatively recently (see Fig.~\ref{fig:fiducial_pdf_distributions}e) and so the high-\achem~disc and bulge are effectively too old to contribute many detectable systems. Nevertheless, we do find a significant fraction of detectable systems originate in the high-\achem~disc and bulge, indicating that it is still important to include these components, as was ignored in some earlier works (see Sec.~\ref{sec:compare_studies}).

@@

\subsection{Formation channels}\label{sec:progenitors_and_formation}
In our fiducial model, approximately two thirds of detectable BHBHs are formed through the `only stable mass transfer' channel \citep{vandenHeuvel+2017}, whilst the remaining third are primarily formed through the `classic' CE channel \citep{Bhattacharya+1991}. Detectable BHNSs follow an inverse pattern, such that around two thirds are formed through the classic channel and the rest are mainly formed through only stable mass transfer.

@@

\subsection{How accurately will we be able to infer the parameters of detected systems?}\label{sec:measurement_uncertainties}
% So far we have discussed the properties of the detectable sources that can, in principle, be inferred from observations. However, many sources will only be barely detectable. Here we discuss for how many systems we expect to get high enough SNR to obtain accurate and useful measurements of these parameters. Below 
Here we discuss the expected SNR distribution and the typical uncertainties expected for the most relevant parameters, namely, the chirp mass and sky localisation.

@@

In Fig.~\ref{fig:snr_dist} we show the cumulative number of detections with a given SNR. Although many LISA sources have SNRs around the our assumed detection threshold of 7, many systems are detection with very high SNRs. We find that for a 4(10)-year LISA mission, of the 124(202) detections, 85(138), 16(27), and 9(14) systems have SNRs greater than 10, 50 and 100, respectively. These high SNR systems are typically, but not only, the more massive BHBH systems.

@@

We find that for a 4(10)-year LISA mission, approximately 41(105) detections have chirp masses ($\Delta \mathcal{M}_c / \mathcal{M}_c < 1$, indicated by the dark shaded region in Fig.~\ref{fig:m_c_unc}) whilst 13(31) have chirp mass uncertainties below 10\%. This uncertainty is generally dominated by the uncertainty on the time derivative of the frequency, since most of the binaries are too early in their inspiral for LISA to measure a strong chirp.
%
Note that increasing the mission length significantly increases the number of detections for which we can measure the mass. The total number of detections only scales as $\sqrt{T_{\rm obs}}$, yet we find that the total number of detections \textit{with well measured masses} scales approximately as $T_{\rm obs}$.

@@

We quantify the sky localisation of a source by estimating the angular resolution for the detectable sources. Since all potential sources are effectively stationary on the timescale of the LISA mission, we can follow \citet{Mandel+2018}, and use the timing accuracy of LISA and the effective detector baseline to calculate the angular resolution, $\sigma_{\theta}$, as
\begin{equation}
    \sigma_{\theta} = 16.6^\circ \left(\frac{7}{\rho}\right) \left(\frac{5 \times 10^{-4} \unit{Hz}}{f_{\rm dom}}\right) \left( \frac{2 \unit{AU}}{L} \right),
\end{equation}
where $L$ is the effective detector baseline, which for LISA is 2 AU since it will orbit the Sun.

@@

For comparison, the size of a pencil beam for a $15 \unit{m}$ diameter SKA dish observing at 1.4 GHz is roughly 0.67 square degrees \citep{Smits+2009}, corresponding to an angular resolution of $\sigma_\theta = \sqrt{(0.67 / \pi)} = 0.46^\circ$ (similar to the angular size of the moon). We will further discuss the prospects of matching LISA detections to radio pulsars with SKA in Sec.~\ref{sec:pulsar_matching}.

### 2021-11-12 paper/tex/sections/variations.tex
all Neige email comments done

We first discuss the robustness of our predictions for the number of detectable systems (Section~\ref{sec:detection_rate_analysis}). We then discuss examples of how the observable properties of the detectable systems, such as the distribution of masses and eccentricities, are affected and can potentially be used to probe about the physics of double compact object formation (Section~\ref{sec:property_variations}).

@@

\subsection{Detection rates}\label{sec:detection_rate_analysis}
In Figure~\ref{fig:detection_rates}, we show the number of LISA detections as predicted by our simulations considering variations in the physical assumptions.  We show predictions for  BHBH, BHNS and NSNS systems in the top, middle and bottom panel respectively. All the rates and their uncertainties plotted in this figure are also provided in Table~\ref{tab:detection_rates}. 
In the sections that follow, we briefly explain the variations considered and discuss the most prominent trends.

@@

For lower mass progenitors, which primarily produce NSNS systems, we find the opposite: increasing $\beta$ leads to an \textit{increase} in the number of detectable NSNS systems. This is in part because the increased mass of the secondary stars allows stars that would have otherwise ended their life as a WD to instead become massive enough to form a NS. The same effect also allows some NS progenitors to become massive enough to BH progenitors, but this effect is less strong. Furthermore, the changes in secondary mass and orbital widening, affects the number of systems for which the reverse interaction successfully ejects the envelope and shrinks the orbit.

\begin{figure*}[p]
    \centering
    \includegraphics[width=\textwidth]{fig9_dco_detections.pdf}
    \caption{The number of expected detections in the LISA mission for different DCO types and model variations. Error bars show the 1- (solid) and 2-$\sigma$ (dotted) Poisson uncertainties. An arrow indicates that the error bar extends to zero. The left axis and grid lines show the number of detections in a 4-year LISA mission and the right axis shows an approximation of the number of detections in a 10-year mission (we scale the axis by $\sqrt{T_{\rm obs}}$, see Table~\ref{tab:detection_rates} for exact rates). Each model is described in further detail in Table~\ref{tab:physics_variations} and details of the fiducial assumptions are in Section~\ref{app:fiducial_physics}. See also Fig.~\ref{fig:dco_relative_rates} and Sec.~\ref{sec:detection_rate_analysis} for a discussion. \href{https://github.com/TomWagg/detecting-DCOs-in-LISA/blob/main/paper/figures/fig9_dco_detections.pdf}{\faFileImage} \href{https://github.com/TomWagg/detecting-DCOs-in-LISA/blob/main/paper/figure_notebooks/detections.ipynb}{\faBook}.}
    \label{fig:detection_rates}
\end{figure*}

@@

\paragraph{The efficiency parameter $\alpha_{\rm CE}$} To estimate the outcome of a CE phase, we use a simple consideration of the binding energy and orbital energy  \citep{Webbink+1984}. Our fiducial model assumes a common-envelope efficiency parameter $\alpha_{\rm CE} = 1$ which can be interpreted as the case where all the energy liberated by shrinking the orbit is used in an optimal way to unbind the envelope \citep{Webbink+1984}. There have been many attempts to constrain this parameter using observations and more recently also using 3D simulations, but no consistent picture has emerged. Therefore we consider variations in this parameter.

@@

Increasing $\alpha_{\rm CE}$ makes common-envelope ejection more efficient or, in other words, less orbital shrinkage is needed to successfully eject the envelope. This has two consequences. (1) Firstly, a larger fraction of systems avoids merging during the CE phase. This increases the overall number of DCOs. (2) Secondly, the systems that survive the CE phase are wider, possibly too wide to become detectable as gravitational wave sources. So, while the first consequence favours the formation of DCOs, the second consequence disfavours the subset that are tight enough to be detected.

@@

In agreement with other studies, we find that this treatment leads to a large increase formation rate of BHBHs and with it the number of systems that LISA can detect. This is because BHBHs originate from the most massive progenitors, which in expand very significantly during the Hertzsprung gap phase in our simulations. The progenitors are likely initiate interaction during this phase. Our predictions for the number of detectable systems increases by a factor 2. The less massive progenitors of BHNSs are less strongly affected, and for NSNS we do not see a significant increase.

@@

We find that not implementing pair-instability supernovae (PISN) ot pulsational pair-instability supernovae (PPISN) in model \modNoPISN{} has no effect on the number of detections with LISA. This is because the average metallicity of the Milky Way is high enough than no progenitor retains enough mass to initiate a PISN or PPISN.

Decreasing the natal kicks for all core-collapse supernovae (models \modSigLow{}-\modSigLower{}) increases the detection rates for each DCO type since lower kicks result in fewer disrupted binaries and hence a more numerous detectable population. The BHNS and NSNS systems are strongly affected whilst the impact on BHBH systems is insignificant. The reason that BHBHs are relatively unaffected is that, in our models, the natal kicks for BHs are scaled down with the amount of mass that falls back. In the case of BHBHs, the black holes have very massive cores and thus low kicks.

@@

Firstly, the decreased winds mean that the DCOs (particularly those containing BHs) are generally more massive and so more detectable in LISA. Secondly, one may expect that LISA sources in model \modWRLow{} would be higher frequency than in our fiducial model as decreased winds generally result in tighter binaries. However, though this is the case at DCO formation, we find by the time the sources have evolved until the LISA mission they are actually at lower frequencies than in our fiducial model. This is because the reduced winds allow DCOs to be formed at higher metallicity and, therefore, at more recent times. This means that the DCOs do not evolve for as long before the LISA mission and so remain at lower frequencies (wider separations) thus making them less detectable.

>>>>

We first discuss the robustness of our predictions for the number of detectable systems (Section~\ref{sec:detection_rate_analysis}). We then discuss examples of how the observable properties of the detectable systems, such as the distribution of masses and eccentricities, are affected and can potentially be used to probe the physics of double compact object formation (Section~\ref{sec:property_variations}).

@@

\subsection{Detection rates}\label{sec:detection_rate_analysis}
In Figure~\ref{fig:detection_rates}, we show the number of LISA detections as calculated by our simulations considering variations in the physical assumptions.  We show the expected number of detections for  BHBH, BHNS and NSNS systems in the top, middle and bottom panel respectively. All the rates and their uncertainties plotted in this figure are also provided in Table~\ref{tab:detection_rates}. 
In the sections that follow, we briefly explain the variations considered and discuss the most prominent trends.

@@

For lower mass progenitors, which primarily produce NSNS systems, we find the opposite: increasing $\beta$ leads to an \textit{increase} in the number of detectable NSNS systems. This is in part because the increased mass of the secondary stars allows stars that would have otherwise ended their life as a WD to instead become massive enough to form a NS. The same effect also allows some NS progenitors to become massive enough to become BH progenitors, but this effect is weaker. Furthermore, the changes in secondary mass and the orbital widening, affect the number of systems for which the reverse interaction successfully ejects the envelope and shrinks the orbit.

\begin{figure*}[p]
    \centering
    \includegraphics[width=\textwidth]{fig9_dco_detections.pdf}
    \caption{The number of expected detections in the LISA mission for different DCO types and model variations. Error bars show the 1- (solid) and 2-$\sigma$ (dotted) Poisson uncertainties. An arrow indicates that the error bar extends to zero. The left axis and grid lines show the number of detections in a 4-year LISA mission and the right axis shows an approximation of the number of detections in a 10-year mission (we scale the axis by $\sqrt{T_{\rm obs}}$, see Table~\ref{tab:detection_rates} for exact rates). Each model is described in further detail in Table~\ref{tab:physics_variations} and details of the fiducial assumptions are in Section~\ref{app:fiducial_physics}. See Sec.~\ref{sec:detection_rate_analysis} for a discussion. \href{https://github.com/TomWagg/detecting-DCOs-in-LISA/blob/main/paper/figures/fig9_dco_detections.pdf}{\faFileImage} \href{https://github.com/TomWagg/detecting-DCOs-in-LISA/blob/main/paper/figure_notebooks/detections.ipynb}{\faBook}.}
    \label{fig:detection_rates}
\end{figure*}

@@

\paragraph{The efficiency parameter $\alpha_{\rm CE}$} To estimate the outcome of a CE phase, we use a simple consideration of the binding energy and orbital energy  \citep{Webbink+1984}. Our fiducial model assumes a common-envelope efficiency parameter $\alpha_{\rm CE} = 1$ which can be interpreted as the case where all the energy liberated by shrinking the orbit is used in an optimal way to unbind the envelope \citep{Webbink+1984}. There have been many attempts to constrain this parameter using observations and more recently also using 3D simulations, but no consistent picture has emerged. Therefore we consider large variations in this parameter.

@@

Increasing $\alpha_{\rm CE}$ makes common-envelope ejection more efficient or, in other words, less orbital shrinkage is needed to successfully eject the envelope. This has two consequences. (1) Firstly, a larger fraction of systems avoids merging during the CE phase. This increases the overall number of DCOs. (2) Secondly, the systems that survive the CE phase are wider, possibly too wide to become detectable as gravitational wave sources. So, while the first consequence favours the formation of DCOs, the second consequence disfavours the formation of DCOs that are tight enough to be detected.

@@

In agreement with other studies, we find that this treatment leads to a large increase formation rate of BHBHs and with it the number of systems that LISA can detect. This is because BHBHs originate from the most massive progenitors, which expand significantly during the Hertzsprung gap phase in our simulations. The progenitors likely initiate interaction during this phase. Our predictions for the number of detectable systems increases by a factor 2. The less massive progenitors of BHNSs are less strongly affected, and for NSNS we do not see a significant increase.

@@

We find that not implementing pair-instability supernovae (PISN) or pulsational pair-instability supernovae (PPISN) in model \modNoPISN{} has no effect on the number of detections with LISA. This is because the average metallicity of the Milky Way is high enough such that no progenitor retains enough mass to initiate a PISN or PPISN.

Decreasing the natal kicks for all core-collapse supernovae (models \modSigLow{}-\modSigLower{}) increases the detection rates for each DCO type, since lower kicks result in fewer disrupted binaries and hence a more numerous detectable population. The BHNS and NSNS systems are strongly affected whilst the impact on BHBH systems is insignificant. The reason that BHBHs are relatively unaffected is that, in our models, the natal kicks for BHs are scaled down with the amount of mass that falls back. In the case of BHBHs, the black holes have very massive cores and thus low kicks.

@@

Firstly, the decreased Wolf-Rayet like winds mean that the DCOs (particularly those containing BHs) are generally more massive and so more detectable in LISA. Secondly, one may expect that LISA sources in model \modWRLow{} would be higher frequency than in our fiducial model as decreased winds generally result in tighter binaries. However, though this is the case at DCO formation, we find that by the time the sources have evolved until the LISA mission they emit GW  at lower frequencies than in our fiducial model. This is because the reduced winds allow DCOs to be formed at higher metallicity and, therefore, at more recent times. This means that the DCOs do not evolve for as long before the LISA mission and so remain at lower frequencies (wider separations) thus making them less detectable.
